HealpixNet: Efficient spherical Convolutional Neural Network with Healpix sampling for cosmological applications

### 2018-07-15 scnn.tex
fix spelling of HEALPix and HealpixNet

Convolutional Neural Networks (CNNs) are now a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
These networks have so far been developed mostly for regular Euclidean domains such as those supporting images, audio, or video.
CNN-based methods are becoming increasingly popular in Cosmology.
Cosmological data often comes in a form of spherical maps, which makes the use of CNNs more complicated.
A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
We present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
We construct a spherical CNNs by representing the sphere as a graph.
Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
For that graph, we define many of the standard CNN operations, such as convolution and pooling, with the filters restricted to being radial.
HealpixNet is a special case of a graph CNN, tailored to the Healpix sampling of the sphere.
% TBD if we include it
% This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
We demonstrate the method on a classification problem of mass maps from two cosmological models.
We compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
We find the performance of HealpixNet to always better or equal to both of these baselines.
For high noise levels and for data covering only a smaller fraction of the sphere, HealpixNet achieves typically 10\% better classification accuracy than those baselines.
Finally, we visualise filters learned by the HealpixNet from the mass maps.
Code and examples are available at \todo{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.

%As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs.
% Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
% In this paper we take the latter view and represent a sampled sphere as a graph, for which we define the convolution and pooling operations.
% Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
% A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
% Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
% \nati{I am not that we should talk about pooling in the abstract. Another angle would be to say that HealPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical structure of the Manifold and b) pooling is natural.}
% While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far.
% As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
% This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
% The filters learned by the HealpixNet are restricted to being radial.
% Michaël: not necessary in the abstract?
% We demonstrate the method on a classification problem of mass maps from two cosmological models.
% \nati{Should we specify what are the baselines? I think not.}
% A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
% HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
% Code and examples are available at \todo{\url{https://github.com/xxx}}.
\end{abstract}

\begin{keyword}
Spherical Convolutional Neural Network \sep SCNN \sep Healpix CNN \sep Graph CNN
\end{keyword}

@@

\todo{@Tomek: can you explain why we care about parts of the sphere? (that is an advantage of the graph model over the spherical harmonics)}
\todo{@Tomek: How is the data acquired? Do telescopes and satellites take measurements according to the Healpix sampling? (it is also an advantage of our method to be agnostic to the sampling, which might be useful to researchers working with missing data or different models)}
\nati{@Tomek: I think what Michael has in mind is that the graph approach is very versatile and extendable. It can be used with other samplings (even irregular ones) or only part of the sphere. This flexibility might be an advantage to mention. In particular, compared to~\citet{cohen2018spherical} it allows us to do only do the required computation when only a part of the sphere is considered.}

@@

In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on Healpix maps. It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the box for cosmological applications.
As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored our method to that particular sampling. However, only two elements depend on the sampling: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
It is also possible to use multiple Healpix maps within our framework and use datasets in form of ``shells''. These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.

@@

The paper is organized as follows.
In \secref{related}, we describe existing approaches to convolutions on spheres, graphs, and manifolds.
\secref{method} exposes the construction of a graph given the Healpix sampling of a sphere and defines the convolution operation.
Finally, \secref{experiments} presents our experimental results on the weak lensing mass map classification problem. There we compare our method to two standard benchmarks and show its superiority.
%We conclude in \secref{conclusion}.

@@

The first approach, leveraging the continuous spherical convolution, has been
proposed by~\cite{cohen2018spherical}. The goal of
these contributions it to use a rotational equivariant convolution on the
sphere, i.e. a rotation of the input implies the same rotation of the output.
The resulting convolution is performed by a spherical Fourier transform (i.e.
a projection on the spherical harmonics), a  multiplication in the spectral
domain and an inverse spherical Fourier transform. Hence the main
computational cost of a convolution comes from the two Fourier transforms.
Fortunately, the Fourier transform can be accelerated for special samplings
set (theoretically including HealPix, \cite{mohlenkamp1999fast,rokhlin2006fast}).
The main advantage of this
approach is that it provides a mathematically well defined rotational
equivariant network. Nevertheless, even with these Fourier transform
acceleration, the convolutions remain expensive in comparison to a traditional
2-dimensional convolution, limiting the practical use of this approach.
\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants
\nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$) For the number, it is a bit more complicated… I guess it is for the next paper.}
}
While a comparison is theoretically possible, the experiments
of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
do not provide any code for the Healpix one. Hence, a practical comparison is
not possible. We also note that this approach cannot be trivially accelerated
if only one part of the sphere is used. This is impractical in the field of
cosmology as the data often observed only on a subpart of the sphere.
One could still pad the unused part of the sphere with 0. However, this would significantly increase the computational cost of the method.
\nati{@mdeff: do you think we can say the method would be too slow for our dataset even without trying it? I am not so sure...}
\todo{slow: full sky maps are composed of millions of points. partial maps are hard to process}

A second direction has been followed in~\citet{boomsma2017spherical}. The idea is
to use the traditional 2-dimensional convolution on an irregular grid defined on the
sphere. In the paper, two grids are used: the equirectangular grid and the ``cubed
sphere'' grid defined by~\citet{ronchi1996cubed}. \nati{Do we need a plot of the equirectangular and cubed sphere sampling?} Because this
approach is based on the traditional 2-dimensional convolution, it is very likely to be the
most computationally efficient one. However, it suffers that it can only be used using very
specific grid sampling sets which are NOT including HealPix. Furthermore, the
grid requirement makes it impossible for the convolution to capture the
spherical properties of the domain, i.e. the "cubed sphere” sampling is by
definition adapted to a cube and not to a sphere.
\todo{border effects? \nati{@mdeff what are you thinking about here?}}
% \nati{Michael: Under some very
% specific hypothesis, this second approach is a particular case of our method,
% i.e. 1) our method with a stupid sampling, 2) assumption that graph convolution
% on a grid == 2d convolution. Do you think we should mention that? I think we
% should not.}
% I think we should!

In an attempt to get the best of the first two approaches, we follow a third
direction. We use a graph to adapt to the particular structure of the sphere.
While the convolution remains efficient, it still captures well the spherical
structure and is particularly adapted to the HealPix sampling.

@@

HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces. A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
In the particular Healpix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.} See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.

@@

\subsection{Problem formulation}
While the number of maps might sound small for deep learning, the information contained in the maps is very recurrent, allowing us to use parts of the map as samples for our simulation.
Leveraging the properties of the HealPix sampling, we can split each maps
into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
As shown in \figref{subpart_sphere}, we used $o=1,2,4$ as the resulting
samples are large enough to suffer from the effects of the spherical geometry. We
decided to only report simulation results for this specific setting as spherical
cosmological data usually does not span the full sphere. Nevertheless, our code
includes an example using the full sphere.

@@

\subsection{Filter visualization}
One common visualization for CNN is to observe the shape of the learned filters.
Since our construction leads to almost (up to the sampling irregularities)
spherical filters, we plot in \figref{learned_filter} both the section (on the
sphere) and a gnomonic projection on a plane of a random selection of learned
filters. The filters are selected from the last layer of the network
corresponding the experiment with order $o=2$ for a relative noise level of
$2$. Nevertheless, all networks presented similar gnomonic and section pattern, at least from a
human perspective. The gnomonic projection clearly exibits the sampling issue
of HealPix. For a detail, on how the convolution kernels are plotted, please refer to Appendix~\ref{sec:filter_visualization}.
\todo{Tomek: can you say something about the filters.}

@@

In this contribution, we presented HealPixNet, a spherical CNN for the HealPix sampling. The gist of our construction resides in using a graph to model the sphere.
This allows us to leverage the advantages of the graph convolution, i.e it is both efficient (with a complexity of $\mathcal{O}(n)$) and flexible (allow to work only on a subpart of the sphere) while it still captures well the spherical properties of the domain.
We also show on a range of classification problems that the neural network systematically significantly outperform classical methods.

The main product of this contribution is HealPixNet,\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} a small and easy-to-use python package for cosmologists to classify sky maps.
As a future work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealPixNet to other spherical CNN using different sampling schemes.

@@

In \figref{gaussian_filters_visualization}, we present three different
visualization for a HealPix graph convolution kernel. The kernel used is defined in the graph spectral domain as $K_t(x)=e^{-\tau t x}$. This is the domain used for our first visualization. In this case, we simply evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. The lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e. the spectral mode with less variation.
As a second visualization, we can observe the kernel directly on the sphere. To do so, we perform the convolution of a
Kroneker on the sphere plot the result with gnomonic projection. Eventually, as we are
working on the sphere with theoretically spherical filters (up to the irregularities of the sampling), we could only plot the section of the convoluted Kroneker. To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}. Note that, because of the small irregularities in the HealPix
sampling, the second and the third methods are subject to small variations depending on the
chosen Kroneker.

>>>>

Convolutional Neural Networks (CNNs) are now a cornerstone of the Deep Learning toolbox and have led to many breakthroughs in Artificial Intelligence.
These networks have so far been developed mostly for regular Euclidean domains such as those supporting images, audio, or video.
CNN-based methods are becoming increasingly popular in Cosmology.
Cosmological data often comes in a form of spherical maps, which makes the use of CNNs more complicated.
A popular format for spherical maps is HEALPix, which uses an equal-area, isolatitude sampling.
We present a spherical CNN for analysis of full and partial HEALPix maps, which we call HealpixNet.
We construct a spherical CNNs by representing the sphere as a graph.
Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
For that graph, we define many of the standard CNN operations, such as convolution and pooling, with the filters restricted to being radial.
HealpixNet is a special case of a graph CNN, tailored to the HEALPix sampling of the sphere.
% TBD if we include it
% This approach is computationally more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
We demonstrate the method on a classification problem of mass maps from two cosmological models.
We compare the performance of the CNN with that of two baseline classifiers, based on the power spectrum and pixel density histogram.
We find the performance of HealpixNet to always better or equal to both of these baselines.
For high noise levels and for data covering only a smaller fraction of the sphere, HealpixNet achieves typically 10\% better classification accuracy than those baselines.
Finally, we visualise filters learned by the HealpixNet from the mass maps.
Code and examples are available at \todo{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.

%As a response to that fact, we are witnessing an increasing interest in the generalization of CNNs to graphs.
% Graphs are versatile data structures which can represent pairwise relationships between objects or act as a discrete representation of a continuous manifold.
% In this paper we take the latter view and represent a sampled sphere as a graph, for which we define the convolution and pooling operations.
% Spherical maps appear in many applications, such as the study of phenomena on the Earth for meteorologists or on the sky for cosmologists.
% A popular format for spherical maps is Healpix, which uses an equal-area, isolatitude sampling.
% Hence, we present a spherical CNN for analysis of full and partial Healpix maps, which we call HealpixNet.
% \nati{I am not that we should talk about pooling in the abstract. Another angle would be to say that HEALPix sampling is well suited for spherical CNN with graphs as a) it is very regular => the graph capture well the spherical structure of the Manifold and b) pooling is natural.}
% While the convolution on arbitrary graphs has mostly been sorted out, a general pooling operation has not been discovered so far.
% As such, while HealpixNet is a special case of a graph CNN, it is tailored to the Healpix sampling of the sphere.
% This approach is computationally much more efficient than using spherical harmonics to perform convolutions, an alternative that has been explored previously.
% The filters learned by the HealpixNet are restricted to being radial.
% Michaël: not necessary in the abstract?
% We demonstrate the method on a classification problem of mass maps from two cosmological models.
% \nati{Should we specify what are the baselines? I think not.}
% A standard benchmark for that problem is to train an SVM on the histograms of map pixel values. Another is to use the power spectral density instead.
% HealpixNet achieves \todo{xx\%} better accuracy than those baselines, is more robust to noise, and is \todo{faster?}.
% Code and examples are available at \todo{\url{https://github.com/xxx}}.
\end{abstract}

\begin{keyword}
Spherical Convolutional Neural Network \sep SCNN \sep HealpixNet \sep Graph CNN
\end{keyword}

@@

\todo{@Tomek: can you explain why we care about parts of the sphere? (that is an advantage of the graph model over the spherical harmonics)}
\todo{@Tomek: How is the data acquired? Do telescopes and satellites take measurements according to the HEALPix sampling? (it is also an advantage of our method to be agnostic to the sampling, which might be useful to researchers working with missing data or different models)}
\nati{@Tomek: I think what Michael has in mind is that the graph approach is very versatile and extendable. It can be used with other samplings (even irregular ones) or only part of the sphere. This flexibility might be an advantage to mention. In particular, compared to~\citet{cohen2018spherical} it allows us to do only do the required computation when only a part of the sphere is considered.}

@@

In this work we present and release HealpixNet\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}, an algorithm and software package which implements an efficient CNN on HEALPix maps. It is implemented with \pkg{TensorFlow} \citep{abadi2016tensorflow} and is intended to be easy to use out-of-the box for cosmological applications.
As HEALPix~\citep{gorski2005healpix} is the most popular sampling used in cosmology and astrophysics, we tailored our method to that particular sampling. However, only two elements depend on the sampling: (i) the choice of neighboring pixels when building the graph, and (ii) the choice of parent pixels when building the hierarchy.
It is also possible to use multiple HEALPix maps within our framework and use datasets in form of ``shells''. These shells can span the radial direction, so that a tomographic analysis can be performed, or different frequencies, in case of data from observations in radio frequencies.

@@

The paper is organized as follows.
In \secref{related}, we describe existing approaches to convolutions on spheres, graphs, and manifolds.
\secref{method} exposes the construction of a graph given the HEALPix sampling of a sphere and defines the convolution operation.
Finally, \secref{experiments} presents our experimental results on the weak lensing mass map classification problem. There we compare our method to two standard benchmarks and show its superiority.
%We conclude in \secref{conclusion}.

@@

The first approach, leveraging the continuous spherical convolution, has been
proposed by~\cite{cohen2018spherical}. The goal of
these contributions it to use a rotational equivariant convolution on the
sphere, i.e. a rotation of the input implies the same rotation of the output.
The resulting convolution is performed by a spherical Fourier transform (i.e.
a projection on the spherical harmonics), a  multiplication in the spectral
domain and an inverse spherical Fourier transform. Hence the main
computational cost of a convolution comes from the two Fourier transforms.
Fortunately, the Fourier transform can be accelerated for special samplings
set (theoretically including HEALPix, \cite{mohlenkamp1999fast,rokhlin2006fast}).
The main advantage of this
approach is that it provides a mathematically well defined rotational
equivariant network. Nevertheless, even with these Fourier transform
acceleration, the convolutions remain expensive in comparison to a traditional
2-dimensional convolution, limiting the practical use of this approach.
\todo{to have numbers to back up our claim: have the theoretical complexities and measure the time needed for a convolution on graph and the healpix Fourier transform to get the constants
\nati{@mdeff: for the complexity we probably have $\mathcal{O}(n)$ instead of $\mathcal{O}(n^{3/2})$ (let assume that we have $\approx n^{1/2}$ points allong both axis, computation of the SO3 FFT is composed of 1) $n^{1/2}$ FFTs for a total cost of $n \log (n)$ and 2) $n^{1/2}$ matrix multiplications of size $n^{1/2}$ for a total cost of $n^{3/2}$) For the number, it is a bit more complicated… I guess it is for the next paper.}
}
While a comparison is theoretically possible, the experiments
of~\cite{cohen2018spherical} are done using the geodesic grid sampling set and
do not provide any code for the HEALPix one. Hence, a practical comparison is
not possible. We also note that this approach cannot be trivially accelerated
if only one part of the sphere is used. This is impractical in the field of
cosmology as the data often observed only on a subpart of the sphere.
One could still pad the unused part of the sphere with 0. However, this would significantly increase the computational cost of the method.
\nati{@mdeff: do you think we can say the method would be too slow for our dataset even without trying it? I am not so sure...}
\todo{slow: full sky maps are composed of millions of points. partial maps are hard to process}

A second direction has been followed in~\citet{boomsma2017spherical}. The idea is
to use the traditional 2-dimensional convolution on an irregular grid defined on the
sphere. In the paper, two grids are used: the equirectangular grid and the ``cubed
sphere'' grid defined by~\citet{ronchi1996cubed}. \nati{Do we need a plot of the equirectangular and cubed sphere sampling?} Because this
approach is based on the traditional 2-dimensional convolution, it is very likely to be the
most computationally efficient one. However, it suffers that it can only be used using very
specific grid sampling sets which are not including HEALPix. Furthermore, the
grid requirement makes it impossible for the convolution to capture the
spherical properties of the domain, i.e. the "cubed sphere” sampling is by
definition adapted to a cube and not to a sphere.
\todo{border effects? \nati{@mdeff what are you thinking about here?}}
% \nati{Michael: Under some very
% specific hypothesis, this second approach is a particular case of our method,
% i.e. 1) our method with a stupid sampling, 2) assumption that graph convolution
% on a grid == 2d convolution. Do you think we should mention that? I think we
% should not.}
% I think we should!

In an attempt to get the best of the first two approaches, we follow a third
direction. We use a graph to adapt to the particular structure of the sphere.
While the convolution remains efficient, it still captures well the spherical
structure and is particularly adapted to the HEALPix sampling.

@@

HEALPix is a particular case of a more general class of schemes which are based on a hierarchical subdivision of a base polyhedron.
%Many discretized maps of the sphere are based on a hierarchical subdivision of a base polyhedron.
Another example is the geodesic grids which are based on geodesic polyhedrons, i.e., polyhedrons made of triangular faces. A counter-example is the equirectangular projection, which is not constructed from a base polyhedron, although it can be subdivided.
In the particular HEALPix case, the base is a rhombic dodecahedron, i.e., a polyhedron made from 12 congruent rhombic faces.\footnote{A rhombus is a quadrilateral whose four sides all have the same length.} See \figref{pooling} for an illustration of the base rhombic dodecahedron and its subdivisions.

@@

\subsection{Problem formulation}
While the number of maps might sound small for deep learning, the information contained in the maps is very recurrent, allowing us to use parts of the map as samples for our simulation.
Leveraging the properties of the HEALPix sampling, we can split each maps
into $12*o^2$ ($o=1,2,4,\dots$) samples that span a smaller part of the sphere.
As shown in \figref{subpart_sphere}, we used $o=1,2,4$ as the resulting
samples are large enough to suffer from the effects of the spherical geometry. We
decided to only report simulation results for this specific setting as spherical
cosmological data usually does not span the full sphere. Nevertheless, our code
includes an example using the full sphere.

@@

\subsection{Filter visualization}
One common visualization for CNN is to observe the shape of the learned filters.
Since our construction leads to almost (up to the sampling irregularities)
spherical filters, we plot in \figref{learned_filter} both the section (on the
sphere) and a gnomonic projection on a plane of a random selection of learned
filters. The filters are selected from the last layer of the network
corresponding the experiment with order $o=2$ for a relative noise level of
$2$. Nevertheless, all networks presented similar gnomonic and section pattern, at least from a
human perspective. The gnomonic projection clearly exibits the sampling issue
of HEALPix. For a detail, on how the convolution kernels are plotted, please refer to Appendix~\ref{sec:filter_visualization}.
\todo{Tomek: can you say something about the filters.}

@@

In this contribution, we presented HealpixNet, a spherical CNN for the HEALPix sampling. The gist of our construction resides in using a graph to model the sphere.
This allows us to leverage the advantages of the graph convolution, i.e it is both efficient (with a complexity of $\mathcal{O}(n)$) and flexible (allow to work only on a subpart of the sphere) while it still captures well the spherical properties of the domain.
We also show on a range of classification problems that the neural network systematically significantly outperform classical methods.

The main product of this contribution is HealpixNet,\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} a small and easy-to-use python package for cosmologists to classify sky maps.
As a future work, we intend to 1) further investigate the link between the graph Fourier basis and the spherical harmonic and 2) compare HealpixNet to other spherical CNN using different sampling schemes.

@@

In \figref{gaussian_filters_visualization}, we present three different
visualization for a HEALPix graph convolution kernel. The kernel used is defined in the graph spectral domain as $K_t(x)=e^{-\tau t x}$. This is the domain used for our first visualization. In this case, we simply evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. The lower eigenvalues $\lambda$ correspond to the lower frequencies, i.e. the spectral mode with less variation.
As a second visualization, we can observe the kernel directly on the sphere. To do so, we perform the convolution of a
Kroneker on the sphere plot the result with gnomonic projection. Eventually, as we are
working on the sphere with theoretically spherical filters (up to the irregularities of the sampling), we could only plot the section of the convoluted Kroneker. To do so, we convolve a Kroneker on the equator and use the equator for our section as shown in~\figref{index_section}. Note that, because of the small irregularities in the HEALPix
sampling, the second and the third methods are subject to small variations depending on the
chosen Kroneker.
